---
title: "R Markdown: A silent movie"
author: "Jaclyn Janis"
output:
  html_document:
    code_folding: hide
---

Today, I'm going to walk you through this R Markdown document to demonstrate its anatomy and functionality, without narrating. Sit back, relax, and take note of the overall process. We'll discuss subsequently.

# Reading in the data

```{r}
library(rmarkdown)
#this is a built-in dataset. See details here:
?swiss

swiss <- swiss
```

This dataframe contains "standardized fertility measure and socio-economic indicators for each of 47 French-speaking provinces of Switzerland at about 1888."

# Let's look at the data

```{r message=FALSE, warning=FALSE}
#First, I'll load my packages.
library(tidyverse)
library(skimr)

# As you see, when I run that code, I receive some messages about those packages, and I don't really feel like seeing those, so I'll change the chunk options to control the output.

#Next, I'll skim the dataframe

skim(swiss)
```

# Let's visualize something

```{r}
swiss %>% 
  #remember how those town names weren't really a column? let's fix that right quick.
  rownames_to_column(var = "Town") %>% 
  #now to the viz
  ggplot(aes(x = Fertility, y = Infant.Mortality, color = Town)) +
  geom_point() +
  coord_flip() +
  theme(legend.position = "none")
```

# Let's make something interactive

You can hover over the points to see the town name and estimates of fertility and infant mortality.

```{r message=FALSE, warning=FALSE}
library(plotly)

#I'm going to save the above visualization as an object
swiss_viz <- swiss %>% 
  rownames_to_column(var = "Town") %>% 
  ggplot(aes(x = Fertility, y = Infant.Mortality, color = Town)) +
  geom_point() +
  coord_flip() +
  theme(legend.position = "none")

ggplotly(swiss_viz)
```

# Conclusion

The mean standardized fertility measure among these towns in 1888 was `r round(mean(swiss$Fertility), 2)`. I really like what I've made, and I think it's worth rendering so I can share it with my collaborators.
